\section{Services}
\label{sec:services}
% Which services are required (confidentiality, authentication, data-integrity, non-repudiation, etc.)
\begin{enumerate}
    % Data can only be read by those who are allowed to read these data
    \item \textbf{Confidentiality}
    \begin{enumerate}
        \item The vote should be private.
        \item Backtracking to the author should not be possible.
    \end{enumerate}
    
    % Guaranteeing the authenticity of a communication
    \item \textbf{Authentication}
    \begin{enumerate}
        \item Only one vote per person can be cast.
        \item Someone should not be be able to vote on one's behalf.
    \end{enumerate}
    
    % Determines which user may access which resources
    \item \textbf{Access control / authorization}
    \begin{enumerate}
        \item The user must be entitled to vote.
        \item Voting should happen within allowed time span.
    \end{enumerate}
    
    % Guarantee that sent data and received data are identical
    \item \textbf{Data integrity}
    \begin{enumerate}
        \item The table is sticky, a cast vote cannot be changed.
        \item One's vote should not be counted twice.
    \end{enumerate}
    
    % For sender:
    % - Sender can’t deny having sent the message
    % - Important for receiver
    %
    % For receiver
    % - Receiver can’t deny having received the message
    % - Important for sender
    \item \textbf{Non-repudiation}
    \begin{enumerate}
        \item Whether or not a person has voted, not which party was voted for.
        \item From government's perspective a vote can not be considered invalid if it has been correctly cast.
        \item The user should have a certificate to prove he has voted (in case the server database crashes)...
        \begin{enumerate}
            \item The server makes a certificate with the users credentials.
            \item The server signs this certificate using his private key.
            \item The server encrypts the certificate using the users public key.
            \item The user receives the certificate for later proof.
        \end{enumerate}
    \end{enumerate}
    
    % System / service is accessible and usable for authorized users
    \item \textbf{Availability}
    \begin{enumerate}
        \item Must be accessible during the complete voting day, since cast votes can't be lost.
        \item The websites/databases will be decentralized. Multiple servers will set-up, in case a server is down the other can be accessed and the voting can continue. 
        \item Some public spaces should be provided with computers for people that do not have direct access to an internet connection.
    \end{enumerate}
\end{enumerate}